Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-07 icdm/submission/includes/evaluation.tex
summary and transition evaluation

\subsection{Convergence time}
To optimize convergence time we have to define it first. Therefore, we used the already available implementation of Gensim \cite{gensim}. Gensim is an open source software that proposes an implementation of the SGNS in Python. It is also written in Cython, therefore it has a fast computation time, but can be used inside a python implementation. Together with the knowledge from Ji et al.\cite{intel} that a score of $0.66$ in the task of word similarity, with the text8 dataset, is the state of the art, we tested Gensim (more on this process in subsection \ref{chap:discussion} and found out that it took 4 epochs to converge. Therefore, we defined the following criteria for convergence: \\
$\rho - \rho_{prev} < 0.009 \vee \rho = 0.66$ \\
where $\rho$ is the Pearson coefficient on the wordsim353 task.
We also stopped computation, if it took more then 20 epochs to converge.

>>>>

\subsection{Convergence time}
To optimize convergence time we have to define it first. Therefore, we used the already available implementation of Gensim \cite{gensim}. Gensim is an open source software that proposes an implementation of the SGNS in Python. It is also written in Cython, therefore it has a fast computation time, but can be used inside a python implementation. Together with the knowledge from Ji et al.\cite{intel} that a score of $0.66$ in the task of word similarity, with the text8 dataset, is the state of the art, we tested Gensim (more on this process in subsection \ref{sec:discussion} and found out that it took 4 epochs to converge. Therefore, we defined the following criteria for convergence: \\
\centerline{$\rho - \rho_{prev} < 0.009 \vee \rho = 0.66$} \\
where $\rho$ is the Pearson coefficient on the wordsim353 task.
We also stopped computation, if it took more then 20 epochs to converge.

To summarize, we deleted words that appear very often (subsampling) and very infrequently (min count) from our dataset, i.e text8 dataset. To evaluate our word embeddings we defined the cosine distance and will compare our embeddings to a human judged dataset of pairs of words based on their similarity. The reader was also given an explanation about the configuration of our network and input shuffling. With all this knowledge we can know present the achieved experimental results in the next section.
